% !TEX TS-program = platex
%!TEX encoding = UTF-8
\documentclass[dvipdfmx,10pt]{beamer}

\usefonttheme{professionalfonts}
\setbeamertemplate{navigation symbols}{}
\setbeamertemplate{footline}[frame number]
\setbeamertemplate{bibliography item}[text]
\usepackage{listings}
\usepackage{amsmath,amsfonts,amsthm,latexsym}
\usepackage{lmodern}
\usepackage{pxjahyper}
\usepackage{cases}
\usepackage{comment}
\usepackage{color,colortbl}
\newtheorem{thm}{Theorem}[section]
\newtheorem{df}[thm]{Definition}
\newtheorem{cor}[thm]{Corollary}
\newcommand{\bb}{\begin{block}}
\newcommand{\eb}{\end{block}}
\newcommand{\ft}{\frametitle}
\newcommand{\ssec}{\subsection}
\newcommand{\sss}{\subsubsection}
\newcommand{\insec}{\insertsection}
\newcommand{\iss}{\insertsubsection}
\newcommand{\isss}{\insertsubsubsection}
\newcommand{\bit}{\begin{itemize}}
\newcommand{\eit}{\end{itemize}}

\usetheme{Berkeley}
\usecolortheme{fly}
\mathversion{bold}
\title{Action plan for the 2020s (Version 1)}
\subtitle{Based on our vision \& mission}
\author[VIA Next Innovators Tokyo]{VIA Next Innovators Tokyo\footnote{\texttt{next\_innovators\_tokyo@viaprograms.org}}}
\date[Jan., 2020]{January, 2020}
\begin{document}
\begin{frame}
\titlepage
\end{frame}
\begin{frame}{Outline}
%https://tex.stackexchange.com/questions/231128/beamer-highlighting-subsubsections-in-toc
  \setcounter{tocdepth}{3}  
  \tableofcontents[
    sectionstyle=show,
    subsectionstyle=show/show,
    subsubsectionstyle=show/show/show
    ]
\end{frame}
\section{Abstract}
\begin{frame}\ft{\insertsection}
\begin{itemize}
\item Plans will be made based on our ideals in the next few years, vision \& mission.
\item Ideals will be determined based on our vision \& mission.
\item Vision \& Mission$\to$Check our outlook documents.
\item We also need strategies for our ideals.
\item Each strategy will have goals.
\item Action principles will be needed$\to$Continue to use the same one. 
\end{itemize}
\end{frame}
\section{Base of our plans for 2020s}
\begin{frame}\ft{\insertsection}
\begin{itemize}
\item Lift up VIA Programs \& VIA Next Innovators to top of social innovators in Japan and US.
\item Japan$\to$Major cities like Tokyo
\item US$\to$Major cities in mainland US 
\item Our focus is concentrated to young people.
\item We will also be the starting point of the social innovation\footnote{We will connect social innovators, change makers and beneficial information.}.
\end{itemize}
\end{frame}
\begin{frame}\ft{\insertsection}
\bb{Strategy}
\begin{itemize}
\item Make VIA Programs \& VIA Next Innovators more famous in Japan \& US.
\item Be and stay active.
\item Maintain the level and quality of ESI/DSI participants.
\end{itemize}
\eb
\begin{alertblock}{What did we change}
More participants$\to$Maintain quality
\end{alertblock}
\bb{Reason}
$$\mathrm{ESI/DSI \ Quality}>\mathrm{Participant \ numbers}$$
\eb
\end{frame}
\begin{frame}\ft{\insertsection}
\bb{Goals for presence}
\begin{itemize}
\item 1000 access per year to our website.
\item Use Google Analytics, google Search Console, Bing WebMaster Tools.
\item Reinforce Search Engine Optimization.
\item 100 views to each document on SlideShare.
\item Constantly post on Facebook, Instagram, etc.
\end{itemize}
\eb
\end{frame}
\begin{frame}\ft{\insertsection}
\begin{itemize}
\item Improve quality of our documents$\to$Maintain ESI/DSI participant quality
\item TO stay active, take beneficial actions on the Internet (Japan \& US).
\item Export our models and belief to other areas.
\end{itemize}
\end{frame}
\section{Action Principles}
\begin{frame}\ft{\insertsection}
\begin{itemize}
\item Be proud of being the part of VIA Programs
\item Expand our networks
\item Know better about VIA Programs
\item Keep Passion and profession
\item Have aspirations
\item Be responsible
\item Enjoy operations
\item Reinforce information disclosure and distribution
\end{itemize}
\end{frame}

\setbeamerfont{frametitle}{size=\Large}
\begin{frame}\ft{Thank You Very Much}
Your attention and interest is appreciated !!!
\bb{Here's our website}
\footnotesize
\texttt{https://sites.google.com/a/viaprograms.org/via-next-innovators-homepage/}
\normalsize
\eb
\end{frame}
\end{document}