% !TEX TS-program = platex
%!TEX encoding = UTF-8
\documentclass[dvipdfmx,10pt]{beamer}

\usefonttheme{professionalfonts}
\setbeamertemplate{navigation symbols}{}
\setbeamertemplate{footline}[frame number]
\setbeamertemplate{bibliography item}[text]
\usepackage{listings}
\usepackage{amsmath,amsfonts,amsthm,latexsym}
\usepackage{lmodern}
\usepackage{hyperref,pxjahyper}
\usepackage{cases}
\usepackage{comment}
\usepackage{color,colortbl}
\newtheorem{thm}{Theorem}[section]
\newtheorem{df}[thm]{Definition}
\newtheorem{cor}[thm]{Corollary}
\newcommand{\bb}{\begin{block}}
\newcommand{\eb}{\end{block}}
\newcommand{\ft}{\frametitle}

\usetheme{Berkeley}
\usecolortheme{albatross}
\setbeamercolor{structure}{fg=cyan}
\setbeamercolor{title}{fg=white,bg=cyan}
\setbeamercolor{author}{fg=cyan}
\setbeamercolor{institute}{fg=cyan}
\setbeamercolor{date}{fg=cyan}
\setbeamercolor{frametitle}{fg=white,bg=cyan}
\setbeamercolor{section in toc}{fg=cyan}
\setbeamercolor{alerted text}{fg=cyan}
\setbeamerfont{alerted text}{series=\bfseries}
\setbeamerfont{section in toc}{series=\mdseries}

\hypersetup{ % hyperref option list
setpagesize=false,
 bookmarksnumbered=true,%
 bookmarksopen=true,%
 colorlinks=true,%
 linkcolor=blue,
 citecolor=cyan,
}

\mathversion{bold}
\title{Welcome 2 ESI}
\subtitle{Explore Social Innovation}
\author[VIA Next Innovators Tokyo]{VIA Next Innovators Tokyo\footnote{\texttt{next\_innovators\_tokyo@viaprograms.org}}}
\institute{Authorized Affiliate of \href{https://viaprograms.org/}{VIA Programs}}
\date[Jan., 2020]{January, 2020}
\begin{document}
\begin{frame}
\titlepage
\end{frame}
\begin{frame}{Outline}
%https://tex.stackexchange.com/questions/231128/beamer-highlighting-subsubsections-in-toc
  \setcounter{tocdepth}{3}  
  \tableofcontents[
    sectionstyle=show,
    subsectionstyle=show/show,
    subsubsectionstyle=show/show/show
    ]
\end{frame}
\section{Abstract of ESI Program}
\begin{frame}\ft{\insertsection}
\footnotesize
\bb{Organizer}
VIA Programs (\texttt{https://viaprograms.org/})
\eb
\bb{Place}
San Francisco Bay Area \& Silicon Valley, United States.
\eb
\bb{Timing}
Every February and August (Approximately 10 days).
\eb
\bb{Events}
\begin{itemize}
\item Workshop at \href{https://dschool.stanford.edu/}{Stanford d.school}.
\item Company visits (\href{https://en.wikipedia.org/wiki/YouTube
}{YouTube}, \href{https://www.baycat.org/}{Baycat}, \href{https://www.kiva.org/}{Kiva},$\cdots$)
\item Design Thinking \& Discussion Sessions.
\item Sharpen your \href{https://en.wikipedia.org/wiki/Leadership}{Leadership}
\item Exchange with Asian Students
\end{itemize}
\eb
\normalsize
\end{frame}
\setbeamerfont{frametitle}{size=\Large}
\begin{frame}\ft{\insertsection}
Excellent Students will Gather From Asia.
\begin{exampleblock}{Affiliations of past participants/coordinators}
\begin{itemize}
\item \href{https://www.u-tokyo.ac.jp/en/}{UT}, \href{https://www.kyoto-u.ac.jp/en/}{Kyoto}, \href{http://www.kyushu-u.ac.jp/en/}{Kyushu}, \href{https://www.osaka-u.ac.jp/en}{Osaka} (Top National Schools in Japan)
\item \href{https://www.keio.ac.jp/en/}{Keio}, \href{https://www.sophia.ac.jp/eng/}{Sophia},$\cdots$ (Top Private Schools in Japan)
\item \href{http://english.pku.edu.cn/}{Peking}, $\cdots$ (Top Schools in Mainland China)
\item \href{https://www.ust.hk/}{HKUST}, \href{https://www.must.edu.mo/en}{MUST},$\cdots$ (Top Schools in HK \& Macau SAR)
\end{itemize}
\end{exampleblock}
\end{frame}
\setbeamerfont{frametitle}{size=\Large}
\begin{frame}\ft{\insertsection}
Great Supporters are Waiting you.
\begin{exampleblock}{People who can help you}
\begin{itemize}
    \item \href{https://sites.google.com/a/viaprograms.org/via-next-innovators-homepage/english-version}{VIA Next Innovators} (based in Japan)
    \item VIA Directors, Fellows \& Coordinators
    \item Alumni Advisors \& Ambassadors
    \item Community Outreach Managers
    \item Mentors
\end{itemize}
\end{exampleblock}
\end{frame}
\setbeamerfont{frametitle}{size=\Large}
\begin{frame}\ft{\insertsection}
\begin{alertblock}{Required Preparations}
\begin{itemize}
\item Submit applications to VIA Programs
\item Interview with ESI staff in English (You will be asked about your previous experiences, academic background, program participation motivations, and expectations)
\item Pre-Program learning
\item Self introduction to other members
\item Obtain your passport, medical insurance, and \href{https://esta.cbp.dhs.gov/}{ESTA}
\end{itemize}
\end{alertblock}
\end{frame}
\setbeamerfont{frametitle}{size=\Large}
\begin{frame}\ft{\insertsection}
Please bring ONE SUITCASE \& ONE SMALL BAG ONLY.
\begin{alertblock}{What to Bring}
\begin{itemize}
\item PASSION, FORWARDNESS, INCENTIVE, MOTIVATION
\item Clothing (Sleepwear,$\cdots$), shoes suitable for walking
\item Prescription Medication
\item Copies of your passport, visa, and medical insurance (STRONGLY REQUIRED)
\item Smartphone (for emergency calls\footnote{For example, \href{https://www.rebtel.com/en/}{Rebtel} is a famous app for cheap international calls and unlimited calling.})
\item Laptop computer or iPad (Internet connection will be OK for most of the program)
\item Credit cards (optional)
\item Electronic English dictionary (optional)
\item Portable umbrella (it could rain during the program)
\end{itemize}
\end{alertblock}
\end{frame}

\section{Keywords \& Key Concepts} 
\setbeamerfont{frametitle}{size=\small}
\begin{frame}\ft{\insertsection}
Ask to us or Mr.Google for details.
\begin{exampleblock}{Social \href{https://en.wikipedia.org/wiki/Entrepreneurship}{Entrepreneurship} \& \href{https://en.wikipedia.org/wiki/Innovation}{Innovation}}
\begin{itemize}
\item Social Innovation\footnote{Murray, R., Caulier-Grice, J., \& Mulgan, G. (2010). The open book of social innovation. London: National endowment for science, technology and the art.}\textsuperscript{,}\footnote{Nicholls, A., Simon, J., Gabriel, M., \& Whelan, C. (Eds.). (2015). New frontiers in social innovation research. Springer.}
\item Social Entrepreneurship\footnote{Mair, J., Robinson, J., \& Hockerts, K. (Eds.). (2006). Social entrepreneurship. New York: Palgrave Macmillan.}\textsuperscript{,}\footnote{Bornstein, D. (2007). How to change the world: Social entrepreneurs and the power of new ideas. Oxford University Press.}\textsuperscript{,}\footnote{Schwartz, B. (2012). Rippling: How social entrepreneurs spread innovation throughout the world. John Wiley \& Sons.}
\item Social Enterprise, \href{https://en.wikipedia.org/wiki/Grassroots}{Grassroots}
\item Collective Impact, Radical Collaboration
\item Minimum Viable Product (MVP)
\end{itemize}
\end{exampleblock}
\end{frame}
\setbeamerfont{frametitle}{size=\Large}
\begin{frame}\ft{\insertsection}
Ask to us or Mr.Google for details.
\begin{exampleblock}{Design Thinking}
\begin{itemize}
    \item Design Thinking\footnote{Cross, N. (2011). Design thinking: Understanding how designers think and work. Berg.}\textsuperscript{,}\footnote{Martin, R., \& Martin, R. L. (2009). The design of business: Why design thinking is the next competitive advantage. Harvard Business Press.}\textsuperscript{,}\footnote{Plattner, H., Meinel, C., \& Leifer, L. (Eds.). (2012). Design thinking research. Springer.}
    \item \href{https://en.wikipedia.org/wiki/Empathy}{Empathy}
    \item \href{https://en.wikipedia.org/wiki/Brainstorming}{Brainstorming}\footnote{Rawlinson, J. G. (2017). Creative thinking and brainstorming. Routledge.}
    \item Iterative Process
\end{itemize}
\end{exampleblock}
\end{frame}
\setbeamerfont{frametitle}{size=\Large}
\begin{frame}\ft{\insertsection}
Ask to us or Mr.Google for details.
\begin{exampleblock}{Business}
\begin{itemize}
    \item Start-Up
    \item \href{https://en.wikipedia.org/wiki/Incubator}{Incubator}
    \item Business Model
    \item Elevator Pitch
    \item Corporate Social Responsibility (CSR)\footnote{Grayson, D., \& Hodges, A. (2017). Corporate social opportunity!: Seven steps to make corporate social responsibility work for your business. Routledge.}
    \item Created Share Value (CSV)
    \item B-Corporation
    \item L3C (Low-profit Limited Liablity Corporation)
    \item Flexible Purpose Corporations
    \item Sharing Economy
\end{itemize}
\end{exampleblock}
\end{frame}
\setbeamerfont{frametitle}{size=\Large}
\begin{frame}\ft{\insertsection}
Ask to us or Mr.Google for details.
\begin{exampleblock}{Investment}
\begin{itemize}
\item \href{https://en.wikipedia.org/wiki/Stakeholder}{Stakeholder}
\item Venture Capital\footnote{Gompers, P. A., \& Lerner, J. (2004). The venture capital cycle. MIT Press.}/Philanthropy\footnote{Saltman, K. (2010). The gift of education: Public education and venture philanthropy. Springer.}
\item Impact Investing\footnote{Vecchi, V., Balbo, L., Brusoni, M., \& Caselli, S. (Eds.). (2017). Principles and practice of impact investing: A catalytic revolution. Routledge.}\textsuperscript{,}\footnote{Logue, D., McAllister, G., \& Schweitzer, J. (2017). Social entrepreneurship and impact investing report. University of Technology Sydney.}
\item Social Impact Bonds
\item Seed Capital
\item \href{https://en.wikipedia.org/wiki/Bootstrapping}{Bootstrapping}
\end{itemize}
\end{exampleblock}
\end{frame}
\begin{frame}\ft{\insertsection}
Ask to us or Mr.Google for details.
\begin{exampleblock}{Measuring Impact}
\begin{itemize}
\item Social Return on Investment (SROI)\footnote{Then, V., Schober, C., Rauscher, O., \& Kehl, K. (2018). Social Return on Investment Analysis: Measuring the Impact of Social Investment. Springer.}
\item \href{https://en.wikipedia.org/wiki/Sustainability}{Sustainability}\footnote{Dresner, S. (2012). The principles of sustainability. Routledge.}\textsuperscript{,}\footnote{Huckle, J., Sterling, S., \& Sterling, S. R. (Eds.). (1996). Education for sustainability. Earthscan.}
\item Triple Bottom-Line (TBL)\footnote{Henriques, A., \& Richardson, J. (Eds.). (2013). The triple bottom line: Does it all add up. Routledge.}$\to$People, Planet, Profit
\end{itemize}
\end{exampleblock}
\end{frame}
\section{Further Reading}
\setbeamerfont{frametitle}{size=\Large}
\begin{frame}\ft{\insertsection}
\footnotesize
\begin{itemize}
    \item Seelig, T. (2012). inGenius: A crash course on creativity. Hay House, Inc.
    \item Westley, F., Zimmerman, B., \& Patton, M. (2009). Getting to maybe: How the world is changed. Vintage Canada.
    \item Prahalad, C. K. (2009). The fortune at the bottom of the pyramid, revised and updated 5th anniversary edition: Eradicating poverty through profits. FT Press.
    \item Lee, N. R., \& Kotler, P. (2015). Social marketing: Changing behaviors for good. Sage Publications.
    \item Kahane, A. (2010). Power and love: A theory and practice of social change. Berrett-Koehler Publishers.
\end{itemize}
\normalsize
\end{frame}
\setbeamerfont{frametitle}{size=\Large}
\begin{frame}\ft{\insertsection}
\footnotesize
\begin{itemize}
        \item Kelley, T. A. (2001). The art of innovation: Lessons in creativity from \href{https://en.wikipedia.org/wiki/IDEO}{IDEO}, America's leading design firm (Vol. 10). Broadway Business.
        \item Strickland, B. (2007). Make the impossible possible: One man's crusade to inspire others to dream bigger and achieve the extraordinary. Crown Business.
        \item Collins, J., \& Porras, J. I. (1995). Visionary companies. Artemis \& Winkler.
        \item Benioff, M., \& Adler, C. (2006). The business of changing the world: Twenty great leaders on strategic corporate philanthropy. McGraw Hill Professional.
        \item Anderson, V., \& Johnson, L. (1997). Systems thinking basics. Cambridge, MA: Pegasus Communications.
        \item Sandel, M. J. (Ed.). (2007). Justice: A reader. Oxford University Press on Demand.
        \item Smith, C. E. (2007). Design with the Other 90\%.
\end{itemize}
\normalsize
\end{frame}
\section{External Links}
\setbeamerfont{frametitle}{size=\small}
\begin{frame}\ft{\insertsection}
\bb{Definitions of Social Innovation}
\begin{itemize}
    \item \href{https://www.gsb.stanford.edu/faculty-research/centers-initiatives/csi/defining-social-innovation}{Defining Social Innovation, Stanford Center for Social Innovation}
    \item \href{http://www.socialinnovationacademy.eu/8-popular-social-innovation-definitions/}{8 popular social innovation definitions by the Social Innovation Academy, published in May 2018.}
\end{itemize}
\eb
\begin{exampleblock}{Related Topics}
\begin{itemize}
    \item Community Organizing\footnote{Rubin, H. J., Rubin, I., \& Doig, R. (1992). Community organizing and development. New York: Macmillan.}\textsuperscript{,}\footnote{Gittell, R., \& Vidal, A. (1998). Community organizing: Building social capital as a development strategy. Sage publications.}
    \item \href{https://en.wikipedia.org/wiki/Mindfulness}{Mindfulness}\footnote{Shapiro, S. L., \& Carlson, L. E. (2009). The art and science of mindfulness: Integrating mindfulness into psychology and the helping professions. American Psychological Association.}\textsuperscript{,}\footnote{Germer, C., Siegel, R. D., \& Fulton, P. R. (Eds.). (2016). Mindfulness and psychotherapy. Guilford Publications.}, \href{https://en.wikipedia.org/wiki/Meditation}{Meditation}
\end{itemize}
\end{exampleblock}
\end{frame}
\section{Contact}
\setbeamerfont{frametitle}{size=\Large}
\begin{frame}\ft{Thank You Very Much}
Your attention and interest is appreciated !!!
\bb{Here's our website}
\footnotesize
\texttt{https://sites.google.com/a/viaprograms.org/via-next-innovators-homepage/}
\normalsize
\eb
\end{frame}
\end{document}